Uncertainty Literature Review

### 2024-01-04 paper.qmd
renamed paper and added notes from meeting

# 4 Uncertainty Visualisation Best Practices
In this section we will first go over the current state of uncertainty visualisation research, which is currently a collection of evaluation studies and review papers, and discuss what it is doing well and what could be done better. Following that, we will provide general reccomendations from the literature.

# 4.1 The current landscape of uncertainty visualisation research
In section 2.1 it was mentioned that uncertainty must be defined within a specific motivating question, otherwise it inherently does not make sense. A large difficulty with the uncertainty visualisation evalusation studies is that this rule is not followed. There are a shockingly large number of evaluation studies that seem to pay no attention to the information that is relevant to the question they are asking, and show participants a selection of seemingly random visualisations from a statistical point of view.

@@

# 4.2 Take aways from the literature

>>>>

In this section we will first go over the current state of uncertainty visualisation research, which is currently a collection of evaluation studies and review papers, and discuss what it is doing well and what could be done better. Following that, we will provide general reccomendations from the literature.

# 4 The current landscape of uncertainty visualisation research
# 4.1 The landscape
In section 2.1 it was mentioned that uncertainty must be defined within a specific motivating question, otherwise it inherently does not make sense. A large difficulty with the uncertainty visualisation evalusation studies is that this rule is not followed. There are a shockingly large number of evaluation studies that seem to pay no attention to the information that is relevant to the question they are asking, and show participants a selection of seemingly random visualisations from a statistical point of view.

@@

# 4.2 Key points from the literature

# 5 Great Examples
- best things you have seen and why they are the best
- can't have a best practices because you need experimental results and my point is that the experiments aren't testing the right things
